Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-31 WRITEUP/ms.tex
extra bracket removed
minor edits

\begin{abstract}
%mm rearranged sentence
We study the properties of molecular cloud complexes (MCs) in a cosmological zoom-in simulation of a
prototypical galaxy (``\flower'') at redshift $z\simeq 6$.
%
We identify MCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
%
In \flower, MC masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc. Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We identify gravitationally unstable MCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter 
%mm (gas+stars), 
    taking into account both gas and stars, 
and by using a more observationally accessible $\alpha_{\rm vir}$ analysis. We find that MCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
%mm
    instability to gravitational 
collapse.
%
%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
%higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
\AF{Abstract is a bit thin. Revise at the end}
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish 
%mm scrutinizing 
data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

Such massive gas inflows trigger gravitational instabilities that lead to the formation of molecular 
%mm complexes [first use of this term; did you want "cloud complexes" instead of "complexes" for agreement with abstract?] 
   cloud complexes (MCCs)  \MM{changed MC to MCC throughout}
that are typically more massive ($M_{\rm cl}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
%
Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

The paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}. We start by providing some physical background in \Sec{Back}. In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower). In \Sec{eqn}, we describe the method used to identify 
%mm molecular gas complexes 
    MCCs,
and present the formalism within which we interpret the results. In \Sec{results}, we present the results and the scaling relations for the MCCs. We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
%
\section{Physical Background}\label{sec:Back}
We begin by introducing some basic material concerning notable physical ("Larson") relations characterizing MCCs, and the gravitational instability of galactic disks, which might be driving MCC formation. Such notions will be used in the subsequent analysis of our simulations. 
\subsection{Larson relations and virial parameter}\label{sec:PVE}
\citet{Larson81a} discussed a number of relations among Galactic 
%mm MCC 
     molecular cloud 
properties, namely the linewidth-size, density-size, and mass-size relations. Larson relations are routinely used for comparing properties of molecular structures in different galactic environments. They also represent a useful framework to analyze our results as they 
%mm
     have been argued to 
arise from the interplay between gravity and turbulence encoded in the virial theorem
%mm 
    (however, note the alternative interpretation involving gravitational collapse by 
    \citealt{Ballesteros-Paredes11}).

%mm In general, the virial theorem for a gas distribution of gas can be written as
     The virial theorem for a distribution of unmagnetized gas can be written as \citep{McKee1992}
\begin{equation}\label{eqn:virial_th_general}
\frac{1}{2}\ddot{\mathcal{I}} = 2(\mathcal{T} - \mathcal{T}_{\rm ext}) + \mathcal{W},
\end{equation}
where $\ddot{\mathcal{I}}$ is the second time derivative of the Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of the gas, $\mathcal{T}_{\rm ext}$ is external pressure support, and $\mathcal{W}$ is the gravitational energy.
%
Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm cl}$, radius $R$, and root-mean-square velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions. 
%mm Neglecting magnetic field and 
Defining $P_{\rm ext}$ as the external pressure, \Eq{virial_th_general} can be written as
\begin{equation}
\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M_{\rm cl} \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM_{\rm cl}^2}{R}\,,
\label{eqn:virial}
\end{equation}
where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the right-hand side represent the
%mm  kinetic, external, and gravity pressure terms. 
    kinetic energy, external pressure, and gravitational potential energy terms.

Motivated by Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a}, we assume equilibrium (i.e.\ ${\ddot{\mathcal{I}}}=0$), define the cloud surface density as
$\Sigma$\eq$M/\pi R^2$, and rewrite the previous equation as 
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \frac{3}{5} \pi G \Sigma \right)\,,
\label{eqn:v0}
\end{equation}
which further reduces to 
\begin{equation}
\frac{\sigma^2}{R} = \frac{\pi}{5} G \Sigma\,,
\label{eqn:SVE}
\end{equation}
if the external pressure $P_{\rm ext}=0$. For this case (often referred to as simple virial equilibrium) from the balance between kinetic and gravity terms we can define the virial parameter as 
\begin{equation}
\alpha_{\rm vir} \equiv  \frac{5\sigma^2R}{GM_{\rm cl}} = \frac{5\sigma^2}{\pi G \Sigma R}\,,
\label{eqn:alpha}
\end{equation}

@@

In our stability analysis, we account for the combined effect of gas and stars 
%mm 
     \citep[derived exactly by][]{Rafikov01}, 
and for the non-negligible disk thickness. This is done by adopting an approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
%
The effect of disk thickness modifies the $Q$ parameter for gas and stars by accounting for the vertical velocity dispersion:
\begin{equation}
T_{x} = \left\{
		\begin{array}{lccr}
			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [1.25em]
			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}        & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r
\\
		\end{array}
	\right.
\end{equation}
and
\begin{equation}
Q^{\rm thick}_{x} = T_{x} Q\,,
\end{equation}
with $x$ indicating either gas or stars.
% Note that w/ thickness, there's the a self-gravity dilution term in the dispersion relation, which in effect reduceds the surface gravity in the vertical direction. As such, it is easier to be stable against gravitaional instability. Thus, the criterion for instability $Q$ is reduced.
%
The combined effect of gas and stars can then be accounted for by writing
\begin{equation}\label{eqn:q_eff}
Q^{-1}_{\rm eff} =  \left\{
				\begin{array}{lccr}
					     {\displaystyle\frac{w}{Q^{\rm thick}_{\star}} + \frac{1}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ }  Q^{\rm thick}_{\star} \geq Q^{\rm thick}_{\rm gas} \\ [0.75em]
                                               {\displaystyle\frac{1}{Q^{\rm thick}_{\star}} + \frac{w}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ } Q^{\rm thick}_{\star} \leq Q^{\rm thick}_{\rm gas} \\
				\end{array}
			    \right.
\end{equation}
where the relative weight $w$ is defined as:
\begin{equation}
w\equiv\frac{2 \sigma_{\star} \sigma_{\rm gas}}{\sigma_{\star}^2 + \sigma_{\rm gas}^2},
\end{equation}
Conceptually, the finite disk thickness reduces the gravity in the vertical direction, thereby making it easier for a system to
%mm obtain
    maintain 
stability, and thus lowering the critical Toomre $Q_{\rm crit}$ from $\simeq$\,1 to 
0.67 \citep{Goldreich65a}.
%
On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus increases
%mm  the criterion of the Toomre
$Q_{\rm crit}$, 
%mm, unless it is dynamically hot to ``compensate''. 
   moreso if the stars have low velocity dispersion.
As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2

% ------------------
\section{Numerical simulations}\label{sec:sim}
The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses}
\citep{Teyssier02a} as the AMR backend. The simulation used here
covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation
zooms in on a target halo of mass $\sim 10^11 \Msun$. The Lagrangian
region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter
%mm (equivalent baryonic) 
mass resolution of $\simeq 6\times 10^4 \Msun$, 
%mm ($1.2 \times 10^4 \Msun$) [expanded out the meaning, but check if
%I have it right]  Such
     equivalent at initial density to a baryonic mass resolution of $1.2
     \times 10^4 \Msun$.  This 
region is spatially refined with a quasi-Lagrangian criterion based on
a mass threshold, so that a cell is refined if its total dark matter
plus baryonic mass exceeds the mass resolution by a factor of
eight. The final finest refined cell in the zoom in region has size
$l_{\rm cell}\simeq$\,30\,pc (at $z = 6$). 
%mm
%    \MM{Is this really the resolution of dark matter particles?  The baryonic mass (i.e.\ gas) resolution depends on the 
%    local density, which would have to be specified here.} \AP{the setting description has been extended}
     Cell sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
%mm 
%     \MM{Nota Bene!} \AP{This note is discussed in details in the following section. In the simulation we do not treat 5--10 cells as MCs, so I would remove the point from the present} although the resolved scale of 5--10 cells is rather larger.
The models include a chemical network 
following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and
H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is
that abundances are calculated using an on-the-fly non-equilibrium
formation of molecular hydrogen scheme  
%mm following \citet{Pallotini17b} [the order had to be reversed for alphabetization]
    described by \citet{Pallottini17a}.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    {\it Top}: Star formation history of \flower. {\it Bottom}:
    projected stellar mass distribution during {\it (a)} an early
    accreting phase;  {\it (b)} a major starburst following a merger
    event; and {\it (c)} a relatively quiescent post-starburst
    phase. \MM{The figure says ``Accreting'', so I have edited
      elsewhere to match.  You could also remove the quote marks from Quiescent.}
\label{fig:SFH}}
\end{figure*}

@@

In the clump-finding process, we employ a set of different density
thresholds defined based on the molecular hydrogen density of \flower
at different evolutionary stages ($z=6.0$--7.2).
%
We note that this process is 
%mm in essence similar
    the three-dimensional analog
to identifying molecular structures based on the noise levels 
%mm of surface density maps
     in position-position-velocity maps that
observers obtain with telescopes, using molecular line tracers such as
CO, CS, and HCN.
%mm , as commonly adopted in observational studies (e.g., 
     This is commonly done by 
identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
%
%We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
Existing studies find a good correspondence in the dynamical
properties extracted in PPV- versus PPP-space 
%mm
   for well-isolated structures 
(\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see
%mm
    \citealt{Ballesteros-Paredes02a} and 
\citealt{Shetty10a} for a discussion on caveats and limitations).
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
\caption{Probability distribution function of the H$_2$ number density
  in \flower during the accreting phase shown in \Fig{SFH}{\em
    (b)}. \MM{PDFs should be normalized to unity by dividing by the
    area under the curve (total number of samples).  A label on the
    y-axis would also be useful, and perhaps minor ticks on the x-axis.}
\label{fig:h2density}}
\end{figure}

@@

In \Fig{h2density}, we show the probability distribution of H$_2$
number density $n_{\rm H2}$ for \flower~ during its accreting phase,
including the contribution from the gas within 3.5 kpc from the
galaxy center. 
%
We note that the distribution is almost flat for $n_{\rm
  H2}\gtrsim1$\,\cc and it samples the range of densities where clumps
are found based on morphological analysis\footnote{For $n_{\rm
    H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$
  density field is significantly larger than zero. This implies that
  the field is made of isolated components. See Fig. 6 in
  \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCCs by
applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm
    cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08,
5.81, 11.36, 18.96, 31.62]$ to each snapshot. 
%mm [I moved the next sentence into the main text from the footnote.]
We also tested variations in
  $n_{\rm cut}$ range and found no qualitative differences (see
  \Sec{ncut}).
%mm
\MM{I am confused how H$_2$ can survive at such low number
  densities.  Is there some sort of hidden clumping factor at work
  here? Or is this due to the neglect of local photodissociating
  radiation? Either way, the point should be mentioned in section 3, I
guess.}
\DL{ncut should be more like molecular gas density, and H2 fraction in each molecular gas is not 100\%, so the ncut here are lower than
 what one expects for purely H2 regions.}

@@

\subsection{Single Evolutionary Stage}  \label{sec:singless}
\AF{Description of the results is very chaotic. You mix evol. phases, properties, ncut, that is physical and numerical issues. Please reorder and make it more logical.}
We first focus on the two most extreme evolutionary stages of \flower---the accreting and starburst phases (see \Sec{sfh}), and identify a set of MCCs in each of them. Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right), respectively. Let us start from analyzing the accretion phase.

@@

% different evolutionary stages
In the scaling relations examined, we find similar MCC properties in
relation to those observed in the nearby Universe between the
accretion phase and the starburst phase of \flower (see
\Fig{larsons_single}). \MM{I'm not entirely sure what this sentence is
  trying to say.  These MCCs don't look similar to nearby objects to
  me... but then you make a comparison between phases?} That is, we do not find any quantitative major differences in the MCC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr. \DL{some MCCs in SB phase have
lower $\alpha_{\rm vir}$ and pressure, but 
is there any significance in that?} \MM{I'd say there is great
significance to that: lower $\alpha_{\rm vir}$ means greater ability to form
stars, exactly what would be expected during a starburst.}

>>>>

\begin{abstract}
%mm rearranged sentence
We study the properties of molecular cloud complexes (MCCs) in a cosmological zoom-in simulation of a
prototypical galaxy (``\flower'') at redshift $z\simeq 6$.
%
We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
%
In \flower, MCC masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc. Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We identify gravitationally unstable MCCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter 
%mm (gas+stars), 
    taking into account both gas and stars, 
and by using a more observationally accessible $\alpha_{\rm vir}$ analysis. We find that MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
%mm
    instability to gravitational 
collapse.
%
%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
%higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
\AF{Abstract is a bit thin. Revise at the end}
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish 
%mm scrutinizing 
data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

Such massive gas inflows trigger gravitational instabilities that lead to the formation of molecular 
%mm complexes [first use of this term; did you want "cloud complexes" instead of "complexes" for agreement with abstract?] 
   cloud complexes (MCCs) 
that are typically more massive ($M_{\rm cl}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
%
Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

The paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}. We start by providing some physical background in \Sec{Back}. In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower). In \Sec{eqn}, we describe the method used to identify 
MCCs,
and present the formalism within which we interpret the results. In \Sec{results}, we present the results and the scaling relations for the MCCs. We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
%
\section{Physical Background}\label{sec:Back}
We begin by introducing some basic material concerning notable physical ("Larson") relations characterizing MCCs, and the gravitational instability of galactic disks, which might be driving MCC formation. Such notions will be used in the subsequent analysis of our simulations. 
\subsection{Larson relations and virial parameter}\label{sec:PVE}
\citet{Larson81a} discussed a number of relations among Galactic 
%mm MCC 
     molecular cloud 
properties, namely the linewidth-size, density-size, and mass-size relations. Larson relations are routinely used for comparing properties of molecular structures in different galactic environments. They also represent a useful framework to analyze our results as they 
%mm
     have been argued to 
arise from the interplay between gravity and turbulence encoded in the virial theorem
%mm 
    (however, note the alternative interpretation involving gravitational collapse by 
    \citealt{Ballesteros-Paredes11a}).

The virial theorem for a distribution of unmagnetized gas can be written as \citep{McKee92a}
\begin{equation}\label{eqn:virial_th_general}
\frac{1}{2}\ddot{\mathcal{I}} = 2(\mathcal{T} - \mathcal{T}_{\rm ext}) + \mathcal{W},
\end{equation}
where $\ddot{\mathcal{I}}$ is the second time derivative of the Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of the gas, $\mathcal{T}_{\rm ext}$ is external pressure support, and $\mathcal{W}$ is the gravitational energy.
%
Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm cl}$, radius $R$, and root-mean-square velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions. 
%mm Neglecting magnetic field and 
Defining $P_{\rm ext}$ as the external pressure, \Eq{virial_th_general} can be written as
\begin{equation}
\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M_{\rm cl} \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM_{\rm cl}^2}{R}\,,
\label{eqn:virial}
\end{equation}
where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the right-hand side represent the
%mm  kinetic, external, and gravity pressure terms. 
    kinetic energy, external pressure, and gravitational potential energy terms.

Motivated by Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a}, we assume equilibrium (i.e.,\ ${\ddot{\mathcal{I}}}=0$), define the cloud surface density as
$\Sigma$\eq$M/\pi R^2$, and rewrite the previous equation as 
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \frac{3}{5} \pi G \Sigma \right)\,,
\label{eqn:v0}
\end{equation}
which further reduces to 
\begin{equation}
\frac{\sigma^2}{R} = \frac{\pi}{5} G \Sigma\,,
\label{eqn:SVE}
\end{equation}
if the external pressure $P_{\rm ext}=0$. For this case (often referred to as simple virial equilibrium) from the balance between kinetic and gravity terms we can define the virial parameter as 
\begin{equation}
\alpha_{\rm vir} \equiv  \frac{5\sigma^2R}{GM_{\rm cl}} = \frac{5\sigma^2}{\pi G \Sigma R}\,,
\label{eqn:alpha}
\end{equation}

@@

In our stability analysis, we account for the combined effect of gas and stars 
%mm 
     \citep[derived exactly by][]{Rafikov01}, 
and for the non-negligible disk thickness. This is done by adopting an approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
%
The effect of disk thickness modifies the $Q$ parameter for gas and stars by accounting for the vertical velocity dispersion:
\begin{equation}
T_{x} = \left\{
		\begin{array}{lccr}
			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [1.25em]
			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}        & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r
\\
		\end{array}
	\right.
\end{equation}
and
\begin{equation}
Q^{\rm thick}_{x} = T_{x} Q\,,
\end{equation}
with $x$ indicating either gas or stars.
% Note that w/ thickness, there's the a self-gravity dilution term in the dispersion relation, which in effect reduceds the surface gravity in the vertical direction. As such, it is easier to be stable against gravitaional instability. Thus, the criterion for instability $Q$ is reduced.
%
The combined effect of gas and stars can then be accounted for by writing
\begin{equation}\label{eqn:q_eff}
Q^{-1}_{\rm eff} =  \left\{
				\begin{array}{lccr}
					     {\displaystyle\frac{w}{Q^{\rm thick}_{\star}} + \frac{1}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ }  Q^{\rm thick}_{\star} \geq Q^{\rm thick}_{\rm gas} \\ [0.75em]
                                               {\displaystyle\frac{1}{Q^{\rm thick}_{\star}} + \frac{w}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ } Q^{\rm thick}_{\star} \leq Q^{\rm thick}_{\rm gas} \\
				\end{array}
			    \right.
\end{equation}
where the relative weight $w$ is defined as:
\begin{equation}
w\equiv\frac{2 \sigma_{\star} \sigma_{\rm gas}}{\sigma_{\star}^2 + \sigma_{\rm gas}^2},
\end{equation}
Conceptually, the finite disk thickness reduces the gravity in the vertical direction, thereby making it easier for a system to
maintain 
stability, and thus lowering the critical Toomre $Q_{\rm crit}$ from $\simeq$\,1 to 
0.67 \citep{Goldreich65a}.
%
On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus increases
$Q_{\rm crit}$, more-so if the stars have low velocity dispersion.
As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2

% ------------------
\section{Numerical simulations}\label{sec:sim}
The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses}
\citep{Teyssier02a} as the AMR backend. The simulation used here
covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation
zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$. The Lagrangian
region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter
%mm (equivalent baryonic) 
mass resolution of $\simeq 6\times 10^4 \Msun$, 
%mm ($1.2 \times 10^4 \Msun$) [expanded out the meaning, but check if
%I have it right]  Such
     equivalent at initial density to a baryonic mass resolution of $1.2
     \times 10^4 \Msun$.  This 
region is spatially refined with a quasi-Lagrangian criterion based on
a mass threshold, so that a cell is refined if its total dark matter
plus baryonic mass exceeds the mass resolution by a factor of
eight. The final finest refined cell in the zoom in region has size
$l_{\rm cell}\simeq$\,30\,pc (at $z = 6$). 
%mm
%    \MM{Is this really the resolution of dark matter particles?  The baryonic mass (i.e.\ gas) resolution depends on the 
%    local density, which would have to be specified here.} \AP{the setting description has been extended}
     Cell sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
%mm 
%     \MM{Nota Bene!} \AP{This note is discussed in details in the following section. In the simulation we do not treat 5--10 cells as MCs, so I would remove the point from the present} although the resolved scale of 5--10 cells is rather larger.
The models include a chemical network 
following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and
H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is
that abundances are calculated using an on-the-fly non-equilibrium
formation of molecular hydrogen scheme  
%mm following \citet{Pallotini17b} [the order had to be reversed for alphabetization]
    described by \citet{Pallottini17a}.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    {\it Top}: Star formation history of \flower. {\it Bottom}:
    projected stellar mass distribution during {\it (a)} an early
    accreting phase;  {\it (b)} a major starburst following a merger
    event; and {\it (c)} a relatively quiescent post-starburst
    phase. 
\label{fig:SFH}}
\end{figure*}

@@

In the clump-finding process (in position-position-position space; PPP), we employ a set of different density
thresholds defined based on the molecular hydrogen density of \flower
at different evolutionary stages ($z=6.0$--7.2).
%
We note that this process is 
the three-dimensional analog
to identifying molecular structures based on the noise levels 
     in position-position-velocity (PPV) maps that
observers obtain with telescopes, using molecular line tracers such as
CO, CS, and HCN.
%mm , as commonly adopted in observational studies (e.g., 
     This is commonly done by 
identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
%
%We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
Existing studies find a good correspondence in the dynamical
properties extracted in PPV- versus PPP-space 
%mm
   for well-isolated structures 
(\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see
%mm
    \citealt{Ballesteros-Paredes02a} and 
\citealt{Shetty10a} for a discussion on caveats and limitations).
% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig. 1 of Beaumount13a). (may be worth putting more thoughts on this after the report is due).

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
\caption{Number distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
    (b)}. 
\label{fig:h2density}}
\end{figure}

@@

In \Fig{h2density}, we show the probability distribution of H$_2$
number density $n_{\rm H2}$ for \flower~ during its accreting phase,
including the contribution from the gas within 3.5 kpc from the
galaxy center. 
%
We note that the distribution is almost flat for $n_{\rm
  H2}\gtrsim1$\,\cc and it samples the range of densities where clumps
are found based on morphological analysis\footnote{For $n_{\rm
    H2}\gtrsim1$\,\cc, the fourth Minkowski functional of the H$_{2}$
  density field is significantly larger than zero. This implies that
  the field is made of isolated components. See Fig. 6 in
  \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCCs by
applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm
    cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08,
5.81, 11.36, 18.96, 31.62]$ to each snapshot. 
%mm [I moved the next sentence into the main text from the footnote.]
We also tested variations in
  $n_{\rm cut}$ range and found no qualitative differences (see
  \Sec{ncut}).
%mm
\MM{I am confused how H$_2$ can survive at such low number
  densities.  Is there some sort of hidden clumping factor at work
  here? Or is this due to the neglect of local photodissociating
  radiation? Either way, the point should be mentioned in section 3, I
guess.}
\DL{ncut should be more like molecular gas density, and H2 fraction in each molecular gas is not 100\%, so the ncut here are lower than
 what one expects for purely H2 regions.}

@@

\subsection{Single Evolutionary Stage}  \label{sec:singless}
\AF{Description of the results is very chaotic. You mix evol. phases, properties, ncut, that is physical and numerical issues. Please reorder and make it more logical.}
We first focus on the two most extreme evolutionary stages of \flower---the accreting and starburst phases (see \Sec{sfh}), and identify a set of MCCs in each of them. Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right), respectively. Let us start from analyzing the accreting phase.

@@

% different evolutionary stages
In the scaling relations examined, we find similar MCC properties in
relation to those observed in the nearby Universe between the
accreting phase and the starburst phase of \flower (see
\Fig{larsons_single}). \MM{I'm not entirely sure what this sentence is
  trying to say.  These MCCs don't look similar to nearby objects to
  me... but then you make a comparison between phases?} That is, we do not find any quantitative major differences in the MCC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr. \DL{some MCCs in SB phase have
lower $\alpha_{\rm vir}$ and pressure, but 
is there any significance in that?} \MM{I'd say there is great
significance to that: lower $\alpha_{\rm vir}$ means greater ability to form
stars, exactly what would be expected during a starburst.}
